Joint Power Allocation and Network Slicing In an End to End O-RAN System

### 2019-10-17 Latex/tex/pr.tex
add fig1
add fig corrected

\section{Introduction}
Recently, O-RAN which is the integration and expansion of C-RAN and xRAN is expected to be a key technology for 5G to enhance RAN performance and solve the challenges in a best way.  
The Idea of O-RAN comes from two opinion. Firstly, according to real-time analytic used for artificial intelligence system, the radio access networks must be evolved to be more open and smarter than previous generations. Furthermore, O-RAN can virtualize elements of the network with  appropriate interfaces \cite{orant}. \newline
The core idea driving C-RAN is to split radio remote head (RRH) and baseband unit (BBU). Several BBUs operating on a cloud server will create a BBU-pool, providing unified baseband signal processing with powerful computing capabilities. Moreover, in O-RAN technology, this separation is implemented\cite{cran1}.
To communicate between BBU-pool and RRHs, fronthaul interface which is fiber link is assumed with limited capacity. Compression of message which is passed through these links, is a consequence of limited fronthaul capacity\cite{frdl,simeone2016cloud}.
In BBU-Pool, using cloud-computing, enhance performance of system by virtualizing resources
into virtual machines (VMs).
Each VM has a computing processor which is mapped to Virtual Network Functions (VNFs) which is processed arrival data. Also VNFs are mapped to physical resource through NS technique\cite{frdl,luong2018novel,luong2018novel1}. 
xRAN technology ,released in April 2018 as a next generation of RAN, has three fundamental features. Control plane is decoupled from User plane. In addition, a modular eNB software stack is built to operate on common-off-the-shelf (COTS) hardware. Moreover, open north-bound and south-bound interfaces is introduced\cite{xran}.
    \includegraphics[scale=0.55]{c2}
  \caption{Network sliced O-RAN system}
Responsibility of wireless systems of the fifth generation covers a wide range types of services. In order to provide the requirement of these services, NS is implemented to virtualize the common physical network into several logical end-to-end networks. Three different types of NS is introduced in \cite{ns1} contains Core Slicing, RAN Slicing and Core-RAN Slicing. In Core-RAN Slicing, each slice of RAN is mapped to slices of Core.    
In this paper, as  mentioned in figure \eqref{fig:c11}, the downlink of O-RAN system is assumed. UEs are divided to different groups according to 

@@

    \includegraphics[scale=0.5]{fig1}

>>>>

\section{Introduction}
Recently, O-RAN which is the integration and expansion of C-RAN and xRAN is expected to be a key technology for 5G to enhance RAN performance and solve the challenges in a best way.  
The Idea of O-RAN comes from two opinion. Firstly, according to real-time analytic used for artificial intelligence system, the radio access networks must be evolved to be more open and smarter than previous generations. Furthermore, O-RAN can virtualize elements of the network with  appropriate interfaces \cite{orant}. \newline
The core idea driving C-RAN is to split radio remote head (RRH) and baseband unit (BBU). Several BBUs operating on a cloud server will create a BBU-pool, providing unified baseband signal processing with powerful computing capabilities. Moreover, in O-RAN technology, this separation is implemented\cite{cran1}.
To communicate between BBU-pool and RRHs, fronthaul interface which is fiber link is assumed with limited capacity. Compression of message which is passed through these links, is a consequence of limited fronthaul capacity\cite{frdl,simeone2016cloud}.
In BBU-Pool, using cloud-computing, enhance performance of system by virtualizing resources
into virtual machines (VMs).
Each VM has a computing processor which is mapped to Virtual Network Functions (VNFs) which is processed arrival data. Also VNFs are mapped to physical resource through NS technique\cite{frdl,luong2018novel,luong2018novel1}. 
\newline
xRAN technology ,released in April 2018 as a next generation of RAN, has three fundamental features. Control plane is decoupled from User plane. In addition, a modular eNB software stack is built to operate on common-off-the-shelf (COTS) hardware. Moreover, open north-bound and south-bound interfaces is introduced\cite{xran}.
\begin{figure}[H]
  \centering
    \includegraphics[scale=0.55]{c2}
  \caption{Network sliced O-RAN system}
  \label{fig:c11}
\end{figure} 
Responsibility of wireless systems of the fifth generation covers a wide range types of services. In order to provide the requirement of these services, NS is implemented to virtualize the common physical network into several logical end-to-end networks. Three different types of NS is introduced in \cite{ns1} contains Core Slicing, RAN Slicing and Core-RAN Slicing. In Core-RAN Slicing, each slice of RAN is mapped to slices of Core. Each slice of RAN consists of RRHs, PRB   
\newline

In this paper, as  depicted in figure \eqref{fig:c11}, the downlink of O-RAN system is assumed. UEs are divided to different groups according to 

@@

    \includegraphics[width=\linewidth]{f1}
